% !TeX program = pdflatex
% !TeX encoding = utf8
% !TeX spellcheck = en_GB
% !BIB program = biber

\documentclass[a4paper]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{siunitx}
\usepackage{hyperref}

\usepackage{csquotes}
\usepackage[style=authoryear,backend=biber]{biblatex} 
\addbibresource{literature.bib}

\DeclareCiteCommand{\citeyear}
{}
{\bibhyperref{\printfield{year}}}
{\multicitedelim}
{}

\DeclareCiteCommand{\citeyear*}
{}
{\bibhyperref{\printfield{year}\printfield{extrayear}}}
{\multicitedelim}
{}

%opening
\title{Decision Support for Route Planning to Reduce Heat Stress Considering the Time of the Day}
\author{}

\begin{document}

\maketitle

\begin{abstract}
	Heat stress is a serious risk, in particular for certain groups like elderly or patients with multiple sclerosis or heart disease. Developments like the ageing of society, the increasing urbanisation (urban heat island effect) and the climate change are increasing the risk that people are affected by heat stress. One way to reduce those risks is to adapt the everyday behaviour, e.g. by performing purchases in the supermarket or pharmacy in the morning or evening when temperatures are lower. 
	
	Therefore we are presenting two different approaches for decision support tools that can help people to adapt their everyday behaviour. At first we're presenting a route planer for pedestrians that can find a route with minimal heat exposure. The second approach we're proposing is a tool that supports the user to select the point in time with a minimal risk of heat stress, considering e.g. the opening hours of a shop. In both cases we are utilizing, among other, remote sensing data of a thermal flight scanner. 
	
	Our results are showing that both approaches are able to reduce the heat exposure and therefore can help people to decrease the risk of heat stress in their everyday life.
\end{abstract}

\input{introduction}

\section{Story}
\begin{itemize}
\item Motivation
\begin{itemize}
\item heat is critical for humans
\item particular problems for risk groups (illness, old, etc)
\item walking to areas often done action in particular to typical locations (shopping, health care, etc)
\item those actions have to be done   
\end{itemize}
\item Problem definition
\begin{itemize}
\item how to minimize the impact of heat stress on walking paths?
\item subdivided into:
\begin{itemize}
\item for a given route?
\item When and how to walk typical routes, e.g. pharmacy, doctor
\end{itemize} 
\end{itemize}
\item method:
\begin{itemize}
\item Goal of this paper: We want to provide a routing method to minimize the heat stress of typical walking actions
\item We do so by providing a value function for heat stress which can be used in route planning
\end{itemize}
\item Evaluation:
\begin{itemize}
\item Our data set
\item Evaluation 1 on routes given date in time.  (pure routing approach) and its metrics
\item Evaluation 2: producing queries for typical walking tasks (our selection) and their evaluation
\item implementation as a demonstrator is produced and available at $homepage$
\end{itemize}
\item Conclusion and contribution
\end{itemize}


\printbibliography

\end{document}
